SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-30 docs/questioning.tex
minor addition
more on policy enforcement

Application attacks that involve {\sc dsl}s constitute an important
subset of the code injection problem, as {\sc dsl}s like {\sc sql} and
{\sc xml} play an significant role in the development of either web or
mobile applications. For example, many applications have interfaces
where a user enters input to interact with the application's data,
thereby interacting with the underlying Relational Database Management
System ({\sc rdbms}). This input can become part of an {\sc sql} query
and executed on the target {\sc rdbms}. A code injection attack that
exploits the vulnerabilities of these interfaces by taking advantage
of input validation issues like incorrectly passed parameters or
incorrect type handling, is called an {\sc sql} injection
attack~\cite{CERT02,MS09,HVO06,SW06}. By using similar techniques
malicious users can perform other exploits based on {\sc dsl}s, like
{\sc xp}ath~\cite{SW06,CDL07,MKS09} and {\sc xml}~\cite{MSM13}. With
this kind of attacks, a malicious user can view sensitive information,
destroy or modify protected data, or even crash the entire
application. {\sc html} is another {\sc dsl} that can be used
for malicious purposes when an application does not properly
handle user supplied data. Based on this vulnerability
an attacker can supply valid {\sc html},
typically via a parameter value, and inject their own
content into the page. {\sc html} injection is mainly associated
with {\sc xss} defects.

@@

As we will see in Subsection~\ref{sec:hybrid},
there are mechanisms that borrow elements from
this approach and examine the syntax trees
of scripts to detect JavaScript-driven {\sc xss}.

@@

A number of the frameworks define policies
based on information and features provided by
the Document Object Model ({\sc dom}) of a web page.
Specifically, developers must place all legitimate
scripts inside {\sc html} elements like {\tt div}.
The web browser (locus {\sc x}), parses the
{\sc dom} tree and executes scripts only when they
are contained in such elements. All other scripts
are treated according to the policies defined
on the server. Frameworks that support the
above functionality are {\sc beep}~\cite{TNH07}
and {\sc dsi}~\cite{NSS06}.
The main problem with the above mechanisms is
that they are vulnerable to non-persistent {\sc xss}
attacks that alter the {\sc dom} of an already rendered
page\footnote{\url{https://www.owasp.org/index.php/DOM_Based_XSS}}
~\cite{APKLM10}.

% There are also frameworks that introduce
% policies directly in the scripts that exist in the server.

@@

\subsubsection{Securing Mashups}

@@

@@

  &   {\it TreeHouse}~\cite{IW12} & 18 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 757–-1218ms & {\sc xss} \\

@@

	&   {\it {\sc met}}~\cite{ELX07} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc xss} \\ 
  % TODO@dimitro: discuss this with Panos?

>>>>

Application attacks that involve {\sc dsl}s constitute an important
subset of the code injection problem, as {\sc dsl}s like {\sc sql} and
{\sc xml} play an significant role in the development of either web or
mobile applications. For example, many applications have interfaces
where a user enters input to interact with the application's data,
thereby interacting with the underlying Relational Database Management
System ({\sc rdbms}). This input can become part of an {\sc sql} query
and executed on the target {\sc rdbms}. A code injection attack that
exploits the vulnerabilities of these interfaces by taking advantage
of input validation issues like incorrectly passed parameters or
incorrect type handling, is called an {\sc sql} injection
attack~\cite{CERT02,MS09,HVO06,SW06}. By using similar techniques
malicious users can perform other exploits based on {\sc dsl}s,
like {\sc xp}ath~\cite{SW06,CDL07,MKS09}, {\sc xml}~\cite{MSM13}
and No{\sc sql}~\cite{SMS13}. With this kind of attacks,
a malicious user can view sensitive information,
destroy or modify protected data, or even crash the entire
application. {\sc html} is another {\sc dsl} that can be used
for malicious purposes when an application does not properly
handle user supplied data. Based on this vulnerability
an attacker can supply valid {\sc html},
typically via a parameter value, and inject their own
content into the page. {\sc html} injection is mainly associated
with {\sc xss} defects.

@@

As we will see in Subsection~\ref{sec:hybrid},
there are mechanisms that borrow elements from
this approach and examine the syntax trees
of scripts to detect JavaScript-driven {\sc xss} attacks.

@@

A number of the frameworks define policies
based on information and features provided by
the Document Object Model ({\sc dom}) of a web page.
Specifically, developers must place all legitimate
scripts inside {\sc html} elements like {\tt div}.
The web browser (locus {\sc x}), parses the
{\sc dom} tree and executes scripts only when they
are contained in such elements. All other scripts
are treated according to the policies defined
on the server. Frameworks that support this
functionality are {\sc beep}~\cite{TNH07}
and {\sc dsi}~\cite{NSS06}. The main problem with
the above mechanisms is that they are vulnerable
to non-persistent {\sc xss} attacks that alter
the {\sc dom} of an already rendered
page\footnote{\url{https://www.owasp.org/index.php/DOM_Based_XSS}}
~\cite{APKLM10}.

Another policy enforcement approach introduces
policies directly either in {\sc html} or JavaScript code
to confine their behavior. {\it BrowserShield}~\cite{RDWDE07}
acts as a proxy on the server side (locus {\sc y}) to
parse the {\sc html} of server responses and identifies
scripts. Then, it rewrites them into safe equivalents
and protect the web user from exploitations
that are based on reported browser vulnerabilities.
{\it ConScript}~\cite{ML10}, {\it CoreScript}~\cite{YCIS07}
and the framework by {\it Phung et al.}~\cite{PSC09}
extend JavaScript with new primitive functions to
provide safe methods to protect potentially vulnerable
JavaScript functions. In both cases, policy enforcement takes
place on the JavaScript engine of the browser (locus {\sc x}).
In this way, {\sc xxs} attacks that take advantage
functions like {\tt eval} and {\tt write} that are
used to assemble innocuous-looking parts into harmful
strings would fail. A critical issue regarding
the above frameworks is that they cannot
define policies that restrict the behavior of third-party
scripts introduced by script inclusion and {\tt iframe}
tags. For instance, consider a web page ({\tt foo.net})
that prints the value of the a query parameter ({\tt query})
from the page's {\sc url} in the web page's content
without escaping the value. A malicious user
can take advantage of this and inject JavaScript code
into the page to steal the user's cookie for this particular
page and send it via an image request to a web site
that he or she controls ({\tt malicious.com}).
This could be achieved by including the following
code fragment to the malicious web site:

\lstset{language=VBScript, basicstyle=\footnotesize\ttfamily,}
\begin{lstlisting}
<iframe style="position:absolute;top:-9999px"
    src="http://foo.net/vulnerable.html?query=
    <script>document.write(
    '<img src=\"http://malicious.com/?c=
    '+encodeURIComponent(document.cookie)+'\">')
    </script>"></iframe>
\end{lstlisting}

\noindent
By using the {\tt iframe} tag, the web user will not
realise the redirection. 
This problem is actually solved by the architectures
presented in Subsubsection~~\ref{sec:mashups}.

%{\it j{\sc csrf}}~\cite{PS11}.

@@

\subsubsection{Securing Mashups}
\label{sec:mashups}

{\it WebJail}~\cite{VDDPJ11}, overcomes this issue
by containing the functionality of third-party scripts.

@@

  % &   {\it {\sc met}}~\cite{ELX07} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc xss} \\ 
  % &   {\it TreeHouse}~\cite{IW12} & 18 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 757–-1218ms & {\sc xss} \\
  \multirow{3}{*}{Securing Mashups}

@@

@@

  \multirow{6}{*}{Training}
